Inference of Heating Properties from ``Hot'' Non-flaring Plasmas in Active Region Cores II. Nanoflare Trains

### 2016-08-26 hot_non-flaring_plasma_2/hot_non-flaring_plasma_2.tex
some final edits before first round of review

%Specify packages
\usepackage{amsmath}
\usepackage{tikz}
\usetikzlibrary{shapes.geometric, arrows}
\usepackage[all]{hypcap}
\usepackage[utf8]{inputenc} %force unicode in bibtex
\usepackage{enumitem}

%Define new commands as needed
\newcommand{\ang}{\AA~}
\defcitealias{barnes_inference_2016}{Paper I}
\renewcommand{\sectionautorefname}{Section}
\renewcommand{\subsectionautorefname}{Subsection}
%\linenumbers
%Set options for list spacing
\setenumerate{noitemsep}
%Set tikz options
\tikzstyle{box} = [rectangle, rounded corners, text centered, draw=black]
\tikzstyle{ghost} = [rectangle, rounded corners, text centered, draw=white]
\tikzstyle{arrow} = [thick, ->, >=stealth]

@@

	\par The emission component above $T_m$ has been the subject of less study, but is likely to be important as the so-called ``smoking gun'' of nanoflare heating since its properties may bear a close link to the actual heating. While many workers \citep{reale_evidence_2009,schmelz_hinode_2009,miceli_x-ray_2012,testa_hinode/eis_2012,del_zanna_elemental_2014,petralia_thermal_2014,schmelz_hot_2015} have claimed evidence of this hot, faint component of the emission measure, poor spectral resolution \citep{testa_temperature_2011,winebarger_defining_2012} and non-equilibrium ionization \citep{bradshaw_explosive_2006,reale_nonequilibrium_2008} have made a positive detection of nanoflare heating difficult. However, \citet{brosius_pervasive_2014} used observations from the \textit{EUNIS-13} sounding rocket to identify relatively faint emission from Fe XIX in a non-flaring active region (AR), suggesting temperatures of $\sim8.9$ MK.

@@

	\par A scaling has been claimed for hot emission with $T>T_m$ such that $\mathrm{EM}\propto T^{-b}$, with $b>0$. This fit is usually done in the range $T_m\lesssim T\lesssim10^{7.2}$. However, measured values of these ``hotward" slopes are poorly constrained due to both the low magnitude of emission and the lack of available spectroscopic data in this temperature range \citep{winebarger_defining_2012}. \citet{warren_systematic_2012} find $7\lesssim b\lesssim10$ with uncertainties of $\pm2.5-3$, for 15 AR cores though \citet{del_zanna_elemental_2014}, using observations from the Solar Maximum Mission, claim larger values for $b$. It must be noted though that reconstructing $\mathrm{EM}(T)$ from spectroscropic and narrow-band observations is non-trivial, with different inversion methods often giving significantly different results \citep{landi_monte_2012,guennou_can_2013,aschwanden_benchmark_2015}.

@@

	\par An analogous approach can be used to investigate the properties of the ``hot" coronal component expected from nanoflare heating, and is the subject of the present series of papers. In \citet{barnes_inference_2016} \citepalias[hereafter]{barnes_inference_2016}, we looked at the hot plasma properties due to a single isolated nanoflare. The effects of heating pulse duration, changes to conductive cooling due to heat flux limiting, differential heating of electrons and ions, and non-equilibrium ionization (NEI) were studied. It was shown that signatures of nanoflare heating are likely to be found in the temperature range $4\lesssim T\lesssim 10$ MK. The prospect of measurable signatures above $10$ MK was found to be diminished for short heating pulses (with duration $<100$ s), NEI, and differential heating of the ions rather than the electrons. It is important to stress for a single nanoflare that while the ``hot'' plasma is present, it cannot actually be detected.

@@

	\par In order to treat the evolution of the electron and ion populations separately, we use a modified version of the usual EBTEL equations. This amounts to computing spatial averages of the two-fluid hydrodynamic equations over both the transition region and corona. A full description and derivation of these equations can be found in the appendix of \citetalias{barnes_inference_2016}. The relevant two-fluid pressure and density equations are,

@@

	where $c_2=\bar{T}_e/T_{e,a}\approx0.9$, $c_3=T_{e,0}/T_{e,a}\approx0.6$, $\nu_{ei}$ is the electron-ion binary Coulomb collision frequency, and $\psi_{TR}$ is a term included to maintain charge and current and neutrality. Additionally, $c_1=\mathcal{R}_{TR}/\mathcal{R}_C$ and its formulation is discussed in \citet{cargill_enthalpy-based_2012} with additional modifications detailed in Appendix 1 of \citetalias{barnes_inference_2016}. These equations are closed by the equations of state $p_e=k_BnT_e$ and $p_i=k_BnT_i$. In the cases where we treat the plasma as a single-fluid, we use the original EBTEL model as described in \citet{klimchuk_highly_2008,cargill_enthalpy-based_2012}.

@@

	\par The loop is heated by a prescribed heating function, applied to either the electrons ($\bar{Q}_e$) or the ions ($\bar{Q}_i$). Both species cool through a combination of thermal conduction ($F_{ce,0},\,F_{ci,0}$) and an enthalpy flux to the lower atmosphere, with the electrons also undergoing radiative cooling ($\mathcal{R_C}$). In the case of conductive cooling, a flux limiter, $F_s=(1/2)fnk_BTV_e$, is imposed to mitigate runaway cooling in a low-density, high-temperature plasma. In all cases we use a saturation limit of $f=1$. See \citetalias{barnes_inference_2016} for a discussion of how $f$ is likely to effect the presence of hot emission in a nanoflare-heated plasma.

@@

		\caption{Examples of four different heating functions: uniform heating amplitudes for $t_N=1000$ s (top), uniform heating amplitudes for $t_N=5000$ s (middle), and heating amplitudes drawn from a power-law distribution with index $\alpha=-1.5$ (bottom). In the bottom panel, the events shown in red have waiting times that depend on the previous event energy while the events shown in blue have uniform wait times. The mean wait time in both cases is $t_N=2000$ s.}

@@

	\par According to the nanoflare heating model of \citet{parker_nanoflares_1988}, turbulent loop footpoint motions twist and stress the field, leading to a buildup and subsequent release of energy. Following \citet{cargill_active_2014}, we let $\varepsilon_i\propto t_{N,i}^{\beta}$, where $\varepsilon_i,t_{N,i}$ are the total energy of event $i$ and waiting time following event $i$, respectively, and $\beta=1$ such that the event energy scales linearly with the waiting time. The reasoning for such an expression is as follows. Bursty, nanoflare heating is thought to arise from the stressing and subsequent relaxation of the coronal field. If a sufficient amount of energy is released into the loop, the field will need enough time to ``unravel'' and ``wind up'' again before the next event such that the subsequent waiting time is large. Conversely, if only a small amount of energy is released, the field will require a shorter unwinding time, resulting in a shorter interval between the subsequent events. Thus, this scaling provides a way to incorporate a more physically motivated heating function into a hydrodynamic model which cannot self-consistently determine the heat input based on the evolving magnetic field. \autoref{fig:heating_funcs} shows the various heating functions used for several example $t_N$ values.

@@

	\par We compute the peak heating rate per event in two different ways: 1) the heating rate is uniform such that $H_i=H_0$ for all $i$ and 2) $H_i$ is chosen from a power-law distribution with index $\alpha$ where $\alpha=-1.5,-2.0,$ or $-2.5$. For the second case, it should be noted that, when $t_N\approx5000$ s, $N\sim16$ events, meaning the events from a single run do not accurately represent the distribution of index $\alpha$. Thus, a sufficiently large number of runs, $N_{R}$, are computed for each $t_N$ to ensure that the total number of events is $N_{tot}=N\times N_{R}\sim10^4$ such that the distribution is well-represented. \autoref{fig:parameter_space} shows the parameter space we will explore. For each set of parameters and waiting time $t_N$, we compute the resulting emission measure distribution for $N$ events in a period $t_{total}$. This procedure is repeated $N_R$ times until $N\times N_R\sim10^4$ is satisfied. Thus, when $t_N=5000$ s and $N\sim16$, $N_R=625$, meaning the model is run 625 times with a heating frequency of $t_N=5000$ s in order to properly fill out the event energy distribution.

@@

	\par When considering the role of nanoflares in the production of hot plasma in AR cores, it is important to take non-equilibrium ionization (NEI) into account \citep{bradshaw_explosive_2006,reale_nonequilibrium_2008}. In a steady heating scenario, the ionization state is an adequate measure of the electron plasma temperature. Because the heating timescale is long (effectively infinite), the ionization state has plenty of time to come into equilibrium with the electron temperature. 

@@

	\par As in \citetalias{barnes_inference_2016}, we use the numerical code\footnote{This code has been made freely available by the author and can be downloaded at: \url{https://github.com/rice-solar-physics/IonPopSolver}.} outlined in \citet{bradshaw_numerical_2009} to asses the impact of NEI on our results. Given a temperature ($T(t)$) and density ($n(t)$) profile from EBTEL, we compute the non-equilibrium ionization states for Fe IX through XXVII and the corresponding effective electron temperature, $T_{eff}$, that would be inferred by assuming ionization equilibrium. Using $T_{eff}$, we are then able to compute a corresponding NEI emission measure distribution, $\mathrm{EM}(T_{eff})$.

@@

	\par We now show the results of our nanoflare train simulations for each point in our multidimensional parameter space: species heated (single-fluid, electron or ion), power-law index ($\alpha$), heating frequency ($t_N$), and waiting-time/event energy relationship ($\beta$). In each 0D hydrodynamic simulation, a loop of half-length $L=40$ Mm is heated by $N$ triangular events of duration $\tau=200$ s and peak heating rate $H_i$ for a duration of $t_{total}=8\times10^4$ s. The average interval between subsequent events is $t_N$ (in the uniform and $\beta=0$ cases, $t_{N,i}=t_N$ exactly for all $i$). We focus primarily on the emission measure distribution, $\mathrm{EM}(T)$, and observables typically calculated from $\mathrm{EM}(T)$. In all cases, the coronal emission measure is calculated according to the method outlined in section 3 of \citetalias{barnes_inference_2016}. The corresponding NEI results, $\mathrm{EM}(T_{eff})$, are calculated similarly, but using $T_{eff}$ (see \autoref{subsec:nei}) instead of $T$. All results were processed using the IPython system for interactive scientific computing in Python \citep{perez_ipython:_2007} as well as the NumPy and Scipy numerical and scientific Python libraries \citep{van_der_walt_numpy_2011}. All results were visualized using the matplotlib graphics library \citep{hunter_matplotlib:_2007}.

@@

		\caption{Emission measure distributions for waiting-times $t_N=250,750,1500,2500,3750,5000$ s in the single-fluid case. The three types of heating functions shown are uniform heating rates (red), heating rates chosen from a power-law distribution of $\alpha=-2.5$ (blue), and heating rates chosen from a power-law distribution of $\alpha=-2.5$ where the time between successive events is proportional to the heating rate of the preceding event (green). Note that in some panels, the blue $\beta=0$ curves may not be visible because they overlap heavily with the green $\beta=1$ curves. The solid lines in the two power law cases show the mean $\mathrm{EM}(T)$ over $N_R$ runs and the shading indicates $1\sigma$ from the mean. The dashed lines denote the corresponding $\mathrm{EM}(T_{eff})$ distribution. The standard deviation is not included in the NEI results.}

@@

	\par We compare $\mathrm{EM}(T)$ for three different types of heating functions, across a sample of six different heating frequencies. \autoref{fig:single_em}, \autoref{fig:el_em}, and \autoref{fig:ion_em} show the emission measure distributions for the single-fluid, electron heating, and ion heating cases respectively. Each panel corresponds to a different waiting time ($t_N$) and includes three different types of heating functions: uniform heating events (red), events chosen from a single power-law distribution of index $\alpha=-2.5$ with constant waiting time ($\beta=0$ case, blue), and a waiting time that depends on the energy released in the preceding event ($\beta=1$ case, green). The dashed lines denote the corresponding NEI cases, $\mathrm{EM}(T_{eff})$. The cases shown in \citetalias{barnes_inference_2016} correspond approximately to the red curves in the lower right panels ($t_N=5000$ s) in each of the three figures since the loop is allowed to cool and drain completely before reheating and a single nanoflare energy is used. 

@@

	\par The behavior of $\mathrm{EM}(T)$ above $T_m$ is more complicated, but because $\mathrm{EM}(T_m)$ and $T_m$ are the same for all parameters, we can make a meaningful comparison between the different heating models. For the single-fluid model and short $t_N$, the emission measure distribution falls off sharply on the hot side for a uniform nanoflare train, but choosing heating events from a power law leads to a broader distribution. This just reflects the different initial temperatures generated with a power-law distribution since $T \simeq H^{2/7}$, where $H$ is the heating rate. As $t_N$ increases, the distribution for uniform heating gradually broadens as the initial temperature rises due to the lower density in which the heating occurs. A similar broadening occurs for power law heating distributions with the $\beta=0$ and $\beta=1$ results showing little difference. Note that the $\beta=0$ curve is barely visible as it overlaps almost completely with the $\beta=1$ curve. Especially interesting in this case are the results with NEI included. For a uniform nanoflare train, NEI plays no role up to $t_N$ = 2500 sec, but above that it restricts the temperatures that can be detected, as shown in \citetalias{barnes_inference_2016}. This hot emission is relocated to cooler temperatures, resulting in a small ``bump'' in the emission measure distribution near 10 MK. On the other hand, NEI plays almost no role in the power-law distributions, for either the $\beta=0$ or $\beta=1$ cases.

@@

	\par When only the ions are heated (\autoref{fig:ion_em}), for intermediate to low heating frequencies (i.e. $t_N\ge1500$ s), $\mathrm{EM}(T)$ in the uniform heating case is truncated below 10 MK and in the power law cases extends to just above 10 MK for the lowest heating frequency ($t_N=5000$ s). This cutoff at lower temperatures is due to the fact that the electrons cannot ``see'' the ions until they have cooled well below their peak temperature. This is discussed in \citetalias{barnes_inference_2016} though in the single-pulse cases, the cutoff occured at lower temperatures. Additionally, in both the uniform and power law cases, the peak of $\mathrm{EM}(T)$ is wider for these low frequencies compared to those shown in the lower right panels of \autoref{fig:single_em} and \autoref{fig:el_em}. NEI now plays no role in any of the cases.

@@

	\par From these results, we see that new information about the heating is potentially available above $T_m$, but unlike at lower temperatures (i.e. $T<T_m$), information about the role of a waiting time is lost. For high frequency nanoflares, there is no plasma above $10^{6.8}$ K in any of the heating scenarios. For intermediate frequency, there is a significant enhancement in the hot emission when a power-law energy distribution is used compared with the uniform heating case. For low frequencies, the enhancement with the power-law distrubution is less noticeable, while for uniform heating both electron and single fluid models show distinctive features in the emission measure distribution. \authorcomment1{Not really sure about this last paragraph here...what are we trying to say? $T>T_m$ offers up more information about the heating, but the frequency determines how much information you get? Reworking the last two sentences: }\authorcomment2{For intermediate heating frequencies, there is a significant enhancement in $\mathrm{EM}(T>T_m)$ for the power law cases relative to the uniform heating case in the single-fluid, electron heating, and ion heating cases. For low frequencies, this discrepancy is less pronounced, though the uniform single-fluid and electron heating cases show distinctive features in $\mathrm{EM}(T)$ near 10 MK.}

@@

		\caption{Example heating (top), temperature (middle), and density (bottom) profiles for the case in which only the electrons are heated with an intermediate heating frequency of $t_N=2500$ s. The three curves shown in each panel correspond to uniform heating rates (red), heating rates chosen from a power-law distribution of $\alpha=-2.5$ (blue), and heating rates chosen from a power-law distribution of $\alpha=-2.5$ where the time between successive events is proportional to the heating rate of the preceding event (green).}

@@

	\par In \citet{cargill_active_2014}, \citetalias{barnes_inference_2016}, and \autoref{subsec:em_dist}, we have suggested that the plasma density prior to the nanoflare occuring is a crucial parameter in determining the emission measure distribution. This arises in two distinct ways. Below $T_m$, the temperature and density at which the nanoflare occurs cuts off the emission at lower temperatures. When combined with an energy-dependent waiting time, this can lead to a range of EM slopes in this region \citep{cargill_active_2014}. Above $T_m$, the initial density determines the temperature increase due to the nanoflare, how quickly the initial hot plasma cools, and whether NEI effects are important. We now examine this further.

@@

	\par In the single-fluid and electron heating cases, while $\mathrm{EM}(T)$ in the uniform and power-law heating cases generally agree for low-frequency heating ($t_N=5000$ s), for intermediate frequencies ($t_N\approx750-2500$ s), the power law cases show an enhanced high-temperature component compared to the uniform case as seen in \autoref{fig:single_em} and \autoref{fig:el_em}. \autoref{fig:nT_sample_profiles} shows sample heating, temperature, and density profiles for an intermediate heating frequency ($t_N=2500$ s), in the case where only the electrons are heated, for the three different types of heating functions. In the uniform heating rate case (red), each event has a maximum heating rate of $H_0$ such that the loop undergoes $N\approx30$ identical heating and cooling cycles, each time reaching a maximum temperature and density of $T_{max,0}$ and $n_{max,0}$, respectively. 

@@

	\par In comparing various heating models, we insist that the total energy injected into the loop is the same for each run (see \autoref{eq:heating_rate_constraint}). When the nanoflare heating rates are distributed according to a power law, there will be many events where $H_i<H_0$ and a few events where $H_i\gg H_0$. These few high energy events lead to $T\gg T_{max,0}$ (blue and green curves) as seen in the middle panel of \autoref{fig:nT_sample_profiles}. Because these events are injected into a plasma that is sufficiently dense due to the draining and cooling times being longer than the time since the previous event, the emission measure is able to ``see'' these hot temperatures, resulting in a $>10$ MK component of $\mathrm{EM}(T)$ (see lower left panel of \autoref{fig:single_em} and \autoref{fig:el_em}). In the uniform case, $T_{max,0}<10$ MK such that $\mathrm{EM}(T)$ has a steep cutoff right at 10 MK. Additionally, we note that the only effect of the longer wait times in the $\beta=1$ case as compared to the $\beta=0$ case is an extended cool emission measure at intermediation frequencies (e.g. $t_N=2500$ s); the hot part of $\mathrm{EM}(T)$ for both power law cases is nearly identical. Thus, the hot and cool sides of the emission measure distribution are largely isolated from one another as they are determined by separate phases of the loop evolution.

@@

	\bibliography{astrophys-abbrev.bib,references.bib}

>>>>

%Specify packages
\usepackage{amsmath}
\usepackage{tikz}
\usetikzlibrary{shapes.geometric, arrows}
\usepackage[all]{hypcap}
\usepackage[utf8]{inputenc} %force unicode in bibtex

%Define new commands as needed
\newcommand{\ang}{\AA~}
\defcitealias{barnes_inference_2016-1}{Paper I}
\renewcommand{\sectionautorefname}{Section}
\renewcommand{\subsectionautorefname}{Subsection}
%Set tikz options
\tikzstyle{box} = [rectangle, rounded corners, text centered, draw=black]
\tikzstyle{ghost} = [rectangle, rounded corners, text centered, draw=white]
\tikzstyle{arrow} = [thick, ->, >=stealth]

@@

	\par The emission component above $T_m$ has been the subject of less study, but is likely to be important as the so-called ``smoking gun'' of nanoflare heating since its properties may bear a close link to the actual heating. While many workers \citep{reale_evidence_2009,schmelz_hinode_2009,miceli_x-ray_2012,testa_hinode/eis_2012,del_zanna_elemental_2014,petralia_thermal_2014,schmelz_hot_2015} have claimed evidence of this hot, faint component of the emission measure, poor spectral resolution \citep{testa_temperature_2011,winebarger_defining_2012} and non-equilibrium ionization \citep{bradshaw_explosive_2006,reale_nonequilibrium_2008} may make a positive detection of nanoflare heating difficult. However, \citet{brosius_pervasive_2014} used observations from the \textit{EUNIS-13} sounding rocket to identify relatively faint emission from Fe XIX in a non-flaring active region (AR), suggesting temperatures of $\sim8.9$ MK.

@@

	\par A scaling has been claimed for hot emission with $T>T_m$ such that $\mathrm{EM}\propto T^{-b}$, with $b>0$. This fit is usually done in the range $T_m\lesssim T\lesssim10^{7.2}$. However, measured values of these ``hotward" slopes are poorly constrained due to both the low magnitude of emission and the lack of available spectroscopic data in this temperature range \citep{winebarger_defining_2012}. \citet{warren_systematic_2012} find $7\lesssim b\lesssim10$ with uncertainties of $\pm2.5-3$, for 15 AR cores though \citet{del_zanna_elemental_2014}, using observations from the Solar Maximum Mission, claim larger values for $b$. It must be noted though that reconstructing $\mathrm{EM}(T)$ from spectroscropic and narrow-band observations is non-trivial, with different inversion methods often giving significantly different results \citep{landi_monte_2012,guennou_can_2013}.

@@

	\par An analogous approach can be used to investigate the properties of the ``hot" coronal component expected from nanoflare heating, and is the subject of the present series of papers. In \citet{barnes_inference_2016-1} \citepalias[hereafter]{barnes_inference_2016-1}, we looked at the hot plasma properties due to a single isolated nanoflare. The effects of heating pulse duration, changes to conductive cooling due to heat flux limiting, differential heating of electrons and ions, and non-equilibrium ionization (NEI) were studied. It was shown that signatures of nanoflare heating are likely to be found in the temperature range $4\lesssim T\lesssim 10$ MK. The prospect of measurable signatures above $10$ MK was found to be diminished for short heating pulses (with duration $<100$ s), NEI, and differential heating of the ions rather than the electrons. It is important to stress for a single nanoflare that while the ``hot'' plasma is present, it cannot actually be detected.

@@

	\par In order to treat the evolution of the electron and ion populations separately, we use a modified version of the usual EBTEL equations. This amounts to computing spatial averages of the two-fluid hydrodynamic equations over both the transition region and corona. A full description and derivation of these equations can be found in the appendix of \citetalias{barnes_inference_2016-1}. The relevant two-fluid pressure and density equations are,

@@

	where $c_2=\bar{T}_e/T_{e,a}\approx0.9$, $c_3=T_{e,0}/T_{e,a}\approx0.6$, $\nu_{ei}$ is the electron-ion binary Coulomb collision frequency, and $\psi_{TR}$ is a term included to maintain charge and current and neutrality. Additionally, $c_1=\mathcal{R}_{TR}/\mathcal{R}_C$ and its formulation is discussed in \citet{cargill_enthalpy-based_2012} with additional modifications detailed in Appendix 1 of \citetalias{barnes_inference_2016-1}. These equations are closed by the equations of state $p_e=k_BnT_e$ and $p_i=k_BnT_i$. In the cases where we treat the plasma as a single-fluid, we use the original EBTEL model as described in \citet{klimchuk_highly_2008,cargill_enthalpy-based_2012}.

@@

	\par The loop is heated by a prescribed heating function, applied to either the electrons ($\bar{Q}_e$) or the ions ($\bar{Q}_i$). Both species cool through a combination of thermal conduction ($F_{ce,0},\,F_{ci,0}$) and an enthalpy flux to the lower atmosphere, with the electrons also undergoing radiative cooling ($\mathcal{R_C}$). In the case of conductive cooling, a flux limiter, $F_s=(1/2)fnk_BTV_e$, is imposed to mitigate runaway cooling in a low-density, high-temperature plasma. In all cases we use a saturation limit of $f=1$. See \citetalias{barnes_inference_2016-1} for a discussion of how $f$ is likely to effect the presence of hot emission in a nanoflare-heated plasma.

@@

		\caption{Examples of four different heating functions: uniform heating amplitudes for $t_N=1000$ s (top), uniform heating amplitudes for $t_N=5000$ s (middle), and heating amplitudes drawn from a power-law distribution with index $\alpha=-1.5$ (bottom). In the bottom panel, the events shown in red have waiting times that depend on the previous event energy while the events shown in blue have uniform waiting times. The average waiting time in both cases is $t_N=2000$ s.}

@@

	\par According to the nanoflare heating model of \citet{parker_nanoflares_1988}, turbulent loop footpoint motions twist and stress the field, leading to a buildup and subsequent release of energy. Following \citet{cargill_active_2014}, we let $\varepsilon_i\propto t_{N,i}^{\beta}$, where $\varepsilon_i,t_{N,i}$ are the total energy of event $i$ and waiting time following event $i$, respectively, and $\beta=1$ such that the event energy scales linearly with the waiting time. The reasoning for such an expression is as follows. Bursty, nanoflare heating is thought to arise from the stressing and subsequent relaxation of the coronal field. If a sufficient amount of energy is released into the loop, the field will need enough time to ``wind up'' again before the next event such that the subsequent waiting time is large. Conversely, if only a small amount of energy is released, the field will require a shorter re-winding time, resulting in a shorter interval between the subsequent events. Thus, this scaling provides a way to incorporate a more physically motivated heating function into a hydrodynamic model which cannot self-consistently determine the heat input based on the evolving magnetic field. \autoref{fig:heating_funcs} shows the various heating functions used for several example $t_N$ values. Note that when $\beta=1$, $t_N$ is the \textit{average} waiting time between events since the waiting time after a particular event $i$ is dependent on the energy of that event.

@@

	\par We compute the peak heating rate per event in two different ways: 1) the heating rate is uniform such that $H_i=H_0$ for all $i$ and 2) $H_i$ is chosen from a power-law distribution with index $\alpha$ where $\alpha=-1.5,-2.0,$ or $-2.5$. For the second case, it should be noted that, when $t_N\approx5000$ s, $N\sim16$ events, meaning the events from a single run do not accurately represent the distribution of index $\alpha$. Thus, a sufficiently large number of runs, $N_{R}$, are computed for each $t_N$ to ensure that the total number of events is $N_{tot}=N\times N_{R}\sim10^4$ such that the distribution is well-represented. \autoref{fig:parameter_space} shows the parameter space we will explore. For each set of parameters and waiting time $t_N$, we compute the resulting emission measure distribution for $N$ events in a period $t_{total}$. This procedure is repeated $N_R$ times until $N\times N_R\sim10^4$ is satisfied. Thus, when $t_N=5000$ s and $N\sim16$, $N_R=625$, meaning the model is run 625 times with a waiting time of $t_N=5000$ s in order to properly fill out the event energy distribution.

@@

	\par When considering the role of nanoflares in the production of hot plasma in AR cores, it is important to take non-equilibrium ionization (NEI) into account \citep{bradshaw_explosive_2006,reale_nonequilibrium_2008,barnes_inference_2016-1}. In a steady heating scenario, the ionization state is an adequate measure of the electron plasma temperature. Because the heating timescale is long (effectively infinite), the ionization state has plenty of time to come into equilibrium with the electron temperature. 

@@

	\par As in \citetalias{barnes_inference_2016-1}, we use the numerical code\footnote{This code has been made freely available by the author and can be downloaded at: \url{https://github.com/rice-solar-physics/IonPopSolver}.} outlined in \citet{bradshaw_numerical_2009} to asses the impact of NEI on our results. Given a temperature ($T(t)$) and density ($n(t)$) profile from EBTEL, we compute the non-equilibrium ionization states for Fe IX through XXVII and the corresponding effective electron temperature, $T_{eff}$, that would be inferred by assuming ionization equilibrium. Using $T_{eff}$, we are then able to compute a corresponding NEI emission measure distribution, $\mathrm{EM}(T_{eff})$.

@@

	\par We now show the results of our nanoflare train simulations for each point in our multidimensional parameter space: species heated (single-fluid, electron or ion), power-law index ($\alpha$), waiting time ($t_N$), and waiting-time/event energy relationship ($\beta$). In each 0D hydrodynamic simulation, a loop of half-length $L=40$ Mm is heated by $N$ triangular events of duration $\tau=200$ s and peak heating rate $H_i$ for a duration of $t_{total}=8\times10^4$ s. The average interval between subsequent events is $t_N$ (in the uniform and $\beta=0$ cases, $t_{N,i}=t_N$ exactly for all $i$). We focus primarily on the emission measure distribution, $\mathrm{EM}(T)$, and observables typically calculated from $\mathrm{EM}(T)$. In all cases, the coronal emission measure is calculated according to the method outlined in section 3 of \citetalias{barnes_inference_2016-1}. The corresponding NEI results, $\mathrm{EM}(T_{eff})$, are calculated similarly, but using $T_{eff}$ (see \autoref{subsec:nei}) instead of $T$. All results were processed using the IPython system for interactive scientific computing in Python \citep{perez_ipython:_2007} as well as the NumPy and Scipy numerical and scientific Python libraries \citep{van_der_walt_numpy_2011}. All results were visualized using the matplotlib graphics library \citep{hunter_matplotlib:_2007}.

@@

		\caption{Emission measure distributions for waiting times $t_N=250,750,1500,2500,3750,5000$ s in the single-fluid case. The three types of heating functions shown are uniform heating rates (red), heating rates chosen from a power-law distribution of $\alpha=-2.5$ (blue), and heating rates chosen from a power-law distribution of $\alpha=-2.5$ where the waiting time after each event is proportional to the heating rate of the event (green). For the last case ($\beta=1$), $t_N$ is the average waiting time for all events. Note that in some panels, the blue $\beta=0$ curves may not be visible because they overlap heavily with the green $\beta=1$ curves. The solid lines in the two power law cases show the mean $\mathrm{EM}(T)$ over $N_R$ runs and the shading indicates $1\sigma$ from the mean. The dashed lines denote the corresponding $\mathrm{EM}(T_{eff})$ distribution. The standard deviation is not included in the NEI results.}

@@

	\par We compare $\mathrm{EM}(T)$ for three different types of heating functions, across a sample of six different heating frequencies. \autoref{fig:single_em}, \autoref{fig:el_em}, and \autoref{fig:ion_em} show the emission measure distributions for the single-fluid, electron heating, and ion heating cases respectively. Each panel corresponds to a different average waiting time ($t_N$) and includes three different types of heating functions: uniform heating events (red), events chosen from a single power-law distribution of index $\alpha=-2.5$ with constant waiting time ($\beta=0$ case, blue), and a waiting time that depends on the energy released in the preceding event ($\beta=1$ case, green). The dashed lines denote the corresponding NEI cases, $\mathrm{EM}(T_{eff})$. The cases shown in \citetalias{barnes_inference_2016-1} correspond approximately to the red curves in the lower right panels ($t_N=5000$ s) in each of the three figures since the loop is allowed to cool and drain completely before reheating and a single nanoflare energy is used. 

@@

	\par The behavior of $\mathrm{EM}(T)$ above $T_m$ is more complicated, but because $\mathrm{EM}(T_m)$ and $T_m$ are the same for all parameters, we can make a meaningful comparison between the different heating models. For the single-fluid model and short $t_N$, the emission measure distribution falls off sharply on the hot side for a uniform nanoflare train, but choosing heating events from a power law leads to a broader distribution. This just reflects the different initial temperatures generated with a power-law distribution since $T \simeq H^{2/7}$, where $H$ is the heating rate. As $t_N$ increases, the distribution for uniform heating gradually broadens as the initial temperature rises due to the lower density in which the heating occurs. A similar broadening occurs for power law heating distributions with the $\beta=0$ and $\beta=1$ results showing little difference. Note that the $\beta=0$ curve is barely visible as it overlaps almost completely with the $\beta=1$ curve. Especially interesting in this case are the results with NEI included. For a uniform nanoflare train, NEI plays no role up to $t_N$ = 2500 sec, but above that it restricts the temperatures that can be detected, as shown in \citetalias{barnes_inference_2016-1}. This hot emission is relocated to cooler temperatures, resulting in a small ``bump'' in the emission measure distribution near 10 MK. On the other hand, NEI plays almost no role in the power-law distributions, for either the $\beta=0$ or $\beta=1$ cases.

@@

	\par When only the ions are heated (\autoref{fig:ion_em}), for intermediate to low heating frequencies (i.e. $t_N\ge1500$ s), $\mathrm{EM}(T)$ in the uniform heating case is truncated below 10 MK and in the power law cases extends to just above 10 MK for the longest waiting time ($t_N=5000$ s). This cutoff at lower temperatures is due to the fact that the electrons cannot ``see'' the ions until they have cooled well below their peak temperature. This is discussed in \citetalias{barnes_inference_2016-1} though in the single-pulse cases, the cutoff occured at lower temperatures. Additionally, in both the uniform and power law cases, the peak of $\mathrm{EM}(T)$ is wider for these low frequencies compared to those shown in the lower right panels of \autoref{fig:single_em} and \autoref{fig:el_em}. NEI now plays no role in any of the cases.

@@

	\par From these results, we see that new information about the heating is potentially available above $T_m$, but unlike at lower temperatures (i.e. $T<T_m$), information about the role of a waiting time is lost. For high frequency nanoflares, there is no plasma above $10^{6.8}$ K in any of the heating scenarios. For intermediate heating frequencies, there is a significant enhancement in $\mathrm{EM}(T>T_m)$ for the power law cases relative to the uniform heating case in the single-fluid, electron heating, and ion heating cases. For low frequencies, this discrepancy is less pronounced, though the uniform single-fluid and electron heating cases show distinctive features in $\mathrm{EM}(T)$ near 10 MK.

@@

		\caption{Example heating (top), temperature (middle), and density (bottom) profiles for the case in which only the electrons are heated with a waiting time of $t_N=2500$ s (i.e. an intermediate heating frequency). The three curves shown in each panel correspond to uniform heating rates (red), heating rates chosen from a power-law distribution of $\alpha=-2.5$ (blue), and heating rates chosen from a power-law distribution of $\alpha=-2.5$ where the time between successive events is proportional to the heating rate of the preceding event (green).}

@@

	\par In \citet{cargill_active_2014}, \citetalias{barnes_inference_2016-1}, and \autoref{subsec:em_dist}, we have suggested that the plasma density prior to the nanoflare occuring is a crucial parameter in determining the emission measure distribution. This arises in two distinct ways. Below $T_m$, the temperature and density at which the nanoflare occurs cuts off the emission at lower temperatures. When combined with an energy-dependent waiting time, this can lead to a range of EM slopes in this region \citep{cargill_active_2014}. Above $T_m$, the initial density determines the temperature increase due to the nanoflare, how quickly the initial hot plasma cools, and whether NEI effects are important. We now examine this further.

@@

	\par In the single-fluid and electron heating cases, while $\mathrm{EM}(T)$ in the uniform and power-law heating cases generally agree for low-frequency heating ($t_N=5000$ s), for intermediate frequencies ($t_N\approx750-2500$ s), the power law cases show an enhanced high-temperature component compared to the uniform case as seen in \autoref{fig:single_em} and \autoref{fig:el_em}. \autoref{fig:nT_sample_profiles} shows sample heating, temperature, and density profiles for an intermediate heating frequency (i.e. a waiting time of $t_N=2500$ s), in the case where only the electrons are heated, for the three different types of heating functions. In the uniform heating rate case (red), each event has a maximum heating rate of $H_0$ such that the loop undergoes $N\approx30$ identical heating and cooling cycles, each time reaching a maximum temperature and density of $T_{max,0}$ and $n_{max,0}$, respectively. 

@@

	\par In comparing various heating models, we insist that the total energy injected into the loop is the same for each run (see \autoref{eq:heating_rate_constraint}). When the nanoflare heating rates are distributed according to a power law, there will be many events where $H_i<H_0$ and a few events where $H_i\gg H_0$. These few high energy events lead to $T\gg T_{max,0}$ (blue and green curves) as seen in the middle panel of \autoref{fig:nT_sample_profiles}. Because these events are injected into a plasma that is sufficiently dense due to the draining and cooling times being longer than the time since the previous event, the emission measure is able to ``see'' these hot temperatures, resulting in a $>10$ MK component of $\mathrm{EM}(T)$ (see lower left panel of \autoref{fig:single_em} and \autoref{fig:el_em}). In the uniform case, $T_{max,0}<10$ MK such that $\mathrm{EM}(T)$ has a steep cutoff right at 10 MK. 

@@

	\bibliography{references.bib}
